Distributed Topology Discovery in Self-Assembled Nano Networks

### 2014-02-19 trunk/PAPER/disr.tex
general fixing
English fixes

\hl{The \emph{DBS} stores information in order to capture the dynamic
behavior of the node in the context of the whole
\disr{} execution phased.| \emph{DBS} information represent node's status and are related to the current execution phase}. 
The \emph{DBS} can have the following values:

@@

The \disr{} approach works with a distributed mechanism which is build
upon an exchange of small packets containing the following fields:
\begin{itemize}
\item \emph{packet\_type}: encodes the meaning of the control packet.
\item \emph{seg\_ID}: \hl{the id of the segment associated to the \disr{} control message}.
\item \emph{src\_id}: the id of the node that originated the packet.
\end{itemize}

For what concerns\emph{packet\_type} field, we can have the following control packets types:
\begin{itemize}
\item{\texttt{STARTING\_SEGMENT\_REQUEST}}: Injected by the bootstrap
node when searching the first segment. 
\item{\texttt{STARTING\_SEGMENT\_CONFIRM}}: used when establishing
the starting segment. 
\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (\hl{which is} not the
first)
\item{\texttt{SEGMENT\_CONFIRM}}: used to establish a segment. 
\item{\texttt{SEGMENT\_CANCEL}}: used to cancel the process of searching a segment along a
specific link.
\end{itemize}

@@

The \disr{} control packets described in the previous subsection trigger
node events, which \hl{eventually} change $DBS$ status according to the
current value of $LED$ variables and the type of packet received.
The main \disr{} phases, together with a reference to the particular
status transition involved are described in the following. As a
convention, we used single letters to refer to one of the \emph{DBS} transitions in
Figure~\ref{fig:state_machine} while the phases are visually
represented in~\ref{fig:disr_events}.

@@

\begin{figure*}
\centering
\begin{tabular}{cccc}
\includegraphics[width=0.23\textwidth]{pictures/seq01.eps} & 
\includegraphics[width=0.23\textwidth]{pictures/seq02.eps} &
\includegraphics[width=0.23\textwidth]{pictures/seq03.eps} & 
\includegraphics[width=0.23\textwidth]{pictures/seq04.eps} \\
(a) & (b) & (c) & (d) \\
\includegraphics[width=0.23\textwidth]{pictures/seq05.eps} &
\includegraphics[width=0.23\textwidth]{pictures/seq06.eps} &
\includegraphics[width=0.23\textwidth]{pictures/seq07.eps} & 
\includegraphics[width=0.23\textwidth]{pictures/seq08.eps} \\
(e) & (f) & (g) & (h) \\
\end{tabular}
\caption{Example of \disr{} segment setup: Nodes' status is labeled as CandidateStarting($Cs$), Candidate ($C$), Free ($F$), Assigned ($A$) or Bootstrap ($B$)}
\label{fig:disr_events}
\end{figure*}

\begin{itemize}
\item{\textbf{Injecting bootstrap request}}: all nodes have an initial
\emph{DBS} status set to \emph{Free}, except for a
 node with status \emph{Bootstrap}, set by some control signal from an
upper layer via $(a)$. When starting, this bootstrap node 
changes its status to \emph{CandidateStarting} $(b)$, injecting a
\texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links
(Figure~\ref{fig:disr_events}-a).

\item{\textbf{Bootnode Broadcasting}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
when $Free$, forwards it to its free links using a flooding mechanism and
becoming $CandidateStarting$ $(g)$.
Each of its free links is then marked as \emph{tvisited} with the segment id
associated to the request. Note that a node that has already received a
\texttt{STARTING\_SEGMENT\_REQUEST} packet can simply ignore further packets
associated to the same request, having already contributed to the
flooding (Figure~\ref{fig:disr_events}-b).
%Note also that each of these packets has a max\_segment\_hops
%field to prevent packets from traveling undefinitively.

\item{\textbf{Confirming the Starting Segment}}: when a \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
the bootstrap node (from a different link, of course), the starting
segment is found. Then the bootstrap node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
packet along the link from which it received the
\texttt{STARTING\_SEGMENT\_REQUEST} and becomes \emph{Assigned} $(l)$. Each
node receiving the confirmation does the same by changing its own status
to \emph{Assigned}(Figure~\ref{fig:disr_events}-c). So the confirmation packet is sent back from
node to node and the starting segment is created (Figure~\ref{fig:disr_events}-d).

@@

\item{\textbf{Injecting Segment Requests}}: Each node in the
\emph{Assigned} status can potentially initiate a new segment request.
So it check its links and if a free link is found it changes its
status to $ActiveSearching$ $(c)$ and then sends
a \texttt{SEGMENT\_REQUEST} across the free link $(c)$ (see
Figure~\ref{fig:disr_events}-e). 
Note that each \emph{Assigned} node can inject the request just after
becoming \emph{Assigned}, i.e. it is not needed that the whole confirmation
process in completed (Figure~\ref{fig:disr_events}-f).
Note also that nodes previously set as \emph{CandidateStarting}, when receive
a \texttt{SEGMENT\_REQUEST} can simply cancel their
status and set themselves as $Candidate$ for that request, since this new
request means that the first starting segment has already been found $(h)$. 
\item{\textbf{Segment Confirmation}}: The segment searching process is successful
when an already \emph{Assigned} node receives the
\texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
sent back along the path that originated the request
(Figure~\ref{fig:disr_events}-g), while the
node remains $Assigned$ \hl{(since it could confirm more segments)}. Each node
previously set as $Candidate$ for that segment id, when receives a confirmation packet changes its status to \emph{Assigned} $(m)$ and send back
the same confirmation until it reaches the initiator of the request,
which then changes from $ActiveSearching$ to $Assigned$ $(d)$.

\item{\textbf{Failing while searching a segment}}: this happen when a node receives a \texttt{SEGMENT\_REQUEST} packet but
matches one of two the following conditions: the node is $Free$ but has no
more suitable free links (thus can’t forward the
\texttt{SEGMENT\_REQUEST})$(f)$; the node
is already \emph{Candidate} with another segment id, i.e. is part of another searching process. In all these cases the node
sends back a \texttt{SEGMENT\_CANCEL} along the incoming link (see at
the bottom of Figure~\ref{fig:disr_events}).
\end{itemize}

@@

In this Section we provide further details about \disr{}
execution model, describing the internal behavior implemented in
each node. Note that this also corresponds exactly to what should be
implemented from the \hl{node-hardware} perspective, as discussed in
Section~\ref{sec:implementation}.

The \emph{LED} variables in each node
($segID$, $visited$, $tvisited$, \emph{link\_visited[]}, \emph{link\_tvisited[]})
are initially set as \texttt{NULL}, so the node and all its links
are considered as \emph{Free}.
The only node that makes an exception is the bootstrap node, initialized
in the \emph{Bootstrap} status. All the subsequent events happening at
each node are the consequence of its current dynamic status (DBS), the
packets received and the internal status represented by the
\emph{LED}. Note that in the following, when using expression like
``has a free link'' or ``free node'' we will assume the relationship between 
$LED$ and $DBS$ discussed in Section~\ref{ssec:disr_data}. Further, for
each packet type all the cases not explicitly listed can simply be
ignored since are associated to invalid/inconsistent events of the
\disr{} execution model. A complete list of these cases can be checked
in the environment simulator source code at~\cite{nanoxim}.

@@

\begin{itemize}
\item The node is $Free$: it should set itself as
\emph{CandidateStarting} and forward the packet along its free links, using
broadcasting and marking these links as $tvisited$ with $segID$ found
in the packet.
\item The node is \emph{CandidateStarting} with the same
\emph{segID} and \emph{src\_id} of the packet is equal to the node id:
this means that the node was the initiator of the request, thus a starting segment has
just been found and should be confirmed sending back a \texttt{STARTING\_SEGMENT\_CONFIRM}
packet.  
\item The node is \emph{CandidateStarting}, with the same \emph{segID} of the
packet but the \emph{src\_id} field is different from the node id: since the node is candidate with the same id, it means
that it already accomplished the task of propagating that kind of
packets, thus can simply ignore the event dropping the packet.  
\item The node is \emph{Candidate}, with a different \emph{segID}: 
this simply means that the \texttt{STARTING\_SEGMENT\_REQUEST} just received is deprecated,
because the node has already accepted a non-starting segment request originated from another \emph{Assigned} node.
\item The node is \emph{Assigned}, with a different \emph{segID}:
same as the previous case.

@@

\begin{itemize}
\item The node is \emph{Assigned}: a segment should be confirmed
sending back a \texttt{SEGMENT\_CONFIRM} packet.
\item The node is \emph{Candidate}: it should discard the packet sending
back a \texttt{SEGMENT\_CANCEL}.
\item The node is \emph{Free} and has free
links: it marks itself as \emph{Candidate} and forwards the \texttt{SEGMENT\_REQUEST}
to one of its free links, according to some internal ordering.
\item The node is \emph{CandidateStarting}: same as being $Free$,
since a segment request circulating in the network indicates that the
starting segment process has been completed.
\end{itemize}

@@

\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}}
When the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
the packet: the node set itself as $Assigned$ to the segment $segID$. Further, it should forward this packet to the link where the
original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
can learn the id of the segment they belong to. Then, \emph{LED} should be
updated from \emph{tvisited} to \emph{visited}.

\subsection{Receiving a \texttt{SEGMENT\_CANCEL}}
When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that the research
for a segment along that path was unsuccessful. But if the
node still has some other free link to try, it should forward a
\texttt{SEGMENT\_REQUEST} to the those links. So a node forwards back
the \texttt{SEGMENT\_CANCEL} packet along the link that originated the
\texttt{SEGMENT\_REQUEST} packet $only$ when there are no more free
links to try. If this is the case, the node modifies its status from
\emph{Candidate} to \emph{Free} and forwards the
\texttt{SEGMENT\_CANCEL} packet to the link from which the request was
received. The process stops when the \texttt{SEGMENT\_CANCEL} packet
reach the starting node that originated the request.

>>>>

\emph{DBS} information represent node status and is related to its
current execution phase in the context of \disr{}.
The \emph{DBS} can have the following values:

@@

The \disr{} approach works with a distributed mechanism which is build
upon an exchange of small control packets containing the following fields:
\begin{itemize}
\item \emph{packet\_type}: encodes the meaning of the control packet.
\item \emph{seg\_ID}: the id of the segment targeted by the \disr{} control message.
\item \emph{src\_ID}: the id of the node that originated the packet.
\item \emph{TTL}: a counter which makes the packet expire after a
given number of retries.
\end{itemize}

As regards the \emph{packet\_type} field, we can have the following control packets types:
\begin{itemize}
\item{\texttt{STARTING\_SEGMENT\_REQUEST}}: Injected by the bootstrap
node when searching the first segment. 
\item{\texttt{STARTING\_SEGMENT\_CONFIRM}}: used when establishing
the starting segment. 
\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (not the first).
\item{\texttt{SEGMENT\_CONFIRM}}: used to establish a segment. 
\item{\texttt{SEGMENT\_CANCEL}}: used to cancel the process of searching a segment along a
specific link.
\end{itemize}

@@

The \disr{} control packets described in the previous subsection trigger
node events, which change \emph{DBS} according to the
current value of \emph{LED} variables and the type of packet received.
The main \disr{} phases, together with a reference to the particular
status transition involved are described in the following. As a
convention, we used single letters to refer to one of the \emph{DBS} transitions in
Figure~\ref{fig:state_machine} while the phases are visually
represented in~\ref{fig:disr_events}.

@@

\begin{figure*}
\centering
\begin{tabular}{cccc}
\includegraphics[width=0.23\textwidth]{pictures/seq01.eps} & 
\includegraphics[width=0.23\textwidth]{pictures/seq02.eps} &
\includegraphics[width=0.23\textwidth]{pictures/seq03.eps} & 
\includegraphics[width=0.23\textwidth]{pictures/seq04.eps} \\
(a) & (b) & (c) & (d) \\
\includegraphics[width=0.23\textwidth]{pictures/seq05.eps} &
\includegraphics[width=0.23\textwidth]{pictures/seq06.eps} &
\includegraphics[width=0.23\textwidth]{pictures/seq07.eps} & 
\includegraphics[width=0.23\textwidth]{pictures/seq08.eps} \\
(e) & (f) & (g) & (h) \\
\end{tabular}
\caption{Example of \disr{} segment setup: Nodes' status is labeled as \emph{CandidateStarting} (\emph{Cs}), \emph{Candidate} (\emph{C}), \emph{Free} (\emph{F}), \emph{Assigned} (\emph{A}) or \emph{Bootstrap} (\emph{B})}
\label{fig:disr_events}
\end{figure*}

\begin{itemize}
\item{\textbf{Injecting bootstrap request}}: all nodes have an initial
\emph{DBS} status set to \emph{Free}, except for a
 node with status \emph{Bootstrap}, set by some control signal from an
upper layer via \emph{(a)}. When starting, this bootstrap node 
changes its status to \emph{CandidateStarting} \emph{(b)}, injecting a
\texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links
(Figure~\ref{fig:disr_events}-a).

\item{\textbf{Bootnode Broadcasting}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
when \emph{Free}, forwards it to its free links using a flooding mechanism and
becoming \emph{CandidateStarting} \emph{(g)}.
Each of its free links is then marked as \emph{tvisited} with the segment id
associated to the request. Note that a node that has already received a
\texttt{STARTING\_SEGMENT\_REQUEST} packet can simply ignore further packets
associated to the same request, having already contributed to the
flooding (Figure~\ref{fig:disr_events}-b).
%Note also that each of these packets has a max\_segment\_hops
%field to prevent packets from traveling undefinitively.

\item{\textbf{Confirming the Starting Segment}}: when a \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
the bootstrap node (from a different link, of course), the starting
segment is found. Then the bootstrap node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
packet along the link from which it received the
\texttt{STARTING\_SEGMENT\_REQUEST} and becomes \emph{Assigned} \emph{(l)}. Each
node receiving the confirmation does the same by changing its own status
to \emph{Assigned}(Figure~\ref{fig:disr_events}-c). So the confirmation packet is sent back from
node to node and the starting segment is created (Figure~\ref{fig:disr_events}-d).

@@

\item{\textbf{Injecting Segment Requests}}: Each node in the
\emph{Assigned} status can potentially initiate a new segment request.
So it check its links and if a free link is found it changes its
status to \emph{ActiveSearching} \emph{(c)} and then sends
a \texttt{SEGMENT\_REQUEST} across the free link \emph{(c)} (see
Figure~\ref{fig:disr_events}-e). 
Note that each \emph{Assigned} node can inject the request just after
becoming \emph{Assigned}, i.e. it is not needed that the whole confirmation
process in completed (Figure~\ref{fig:disr_events}-f).
Note also that nodes previously set as \emph{CandidateStarting}, when receive
a \texttt{SEGMENT\_REQUEST} can simply cancel their
status and set themselves as \emph{Candidate} for that request, since this new
request means that the first starting segment has already been found \emph{(h)}. 
\item{\textbf{Segment Confirmation}}: The segment searching process is successful
when an already \emph{Assigned} node receives the
\texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
sent back along the path that originated the request
(Figure~\ref{fig:disr_events}-g), while the
node remains \emph{Assigned} (since it could confirm other segments). Each node
previously set as \emph{Candidate} for that segment id, when receives a confirmation packet changes its status to \emph{Assigned} \emph{(m)} and send back
the same confirmation until it reaches the initiator of the request,
which then changes from \emph{ActiveSearching} to \emph{Assigned} \emph{(d)}.

\item{\textbf{Failing while searching a segment}}: this happen when a node receives a \texttt{SEGMENT\_REQUEST} packet but
matches one of two the following conditions: the node is \emph{Free} but has no
more suitable free links (thus can’t forward the
\texttt{SEGMENT\_REQUEST})\emph{(f)}; the node
is already \emph{Candidate} with another segment id, i.e. is part of another searching process. In all these cases the node
sends back a \texttt{SEGMENT\_CANCEL} along the incoming link (see at
the bottom of Figure~\ref{fig:disr_events}).
\end{itemize}

@@

In this Section we provide further details about \disr{}
execution model, describing the internal behavior implemented in
each node. Note that this also corresponds exactly to what should be
implemented from the hardware perspective, as discussed in
Section~\ref{sec:implementation}.

The \emph{LED} variables in each node
(\emph{segID}, \emph{visited}, \emph{tvisited}, \emph{link\_visited[]}, \emph{link\_tvisited[]})
are initially set as \texttt{NULL}, so the node and all its links
are considered as \emph{Free}.
The only node that makes an exception is the bootstrap node, initialized
in the \emph{Bootstrap} status. All the subsequent events happening at
each node are the consequence of its current dynamic status (DBS), the
packets received and the internal status represented by the
\emph{LED}. Note that in the following, when using expression like
``has a free link'' or ``free node'' we will assume the relationship between 
\emph{LED} and \emph{DBS} discussed in Section~\ref{ssec:disr_data}. Further, for
each packet type all the cases not explicitly listed can simply be
ignored since are associated to invalid/inconsistent events of the
\disr{} execution model. A complete list of these cases can be checked
in the environment simulator source code at~\cite{nanoxim}.

@@

\begin{itemize}
\item The node is \emph{Free}: it should set itself as
\emph{CandidateStarting} and forward the packet along its free links, using
broadcasting and marking these links as \emph{tvisited} with \emph{segID} found
in the packet.
\item The node is \emph{CandidateStarting} with the same
\emph{segID} and \emph{src\_id} of the packet is equal to the node id:
this means that the node was the initiator of the request, thus a starting segment has
just been found and should be confirmed sending back a \texttt{STARTING\_SEGMENT\_CONFIRM}
packet.  
\item The node is \emph{CandidateStarting}, with the same \emph{segID} of the
packet but the \emph{src\_id} field is different from the node id: since the node is candidate with the same id, it means
that it already accomplished the task of propagating that kind of
packets, thus can simply ignore the event dropping the packet.  
\item The node is \emph{Candidate}, with a different \emph{segID}: 
this simply means that the \texttt{STARTING\_SEGMENT\_REQUEST} just received is deprecated,
because the node has already accepted a non-starting segment request originated from another \emph{Assigned} node.
\item The node is \emph{Assigned}, with a different \emph{segID}:
same as the previous case.

@@

\begin{itemize}
\item The node is \emph{Assigned}: a segment should be confirmed
sending back a \texttt{SEGMENT\_CONFIRM} packet.
\item The node is \emph{Candidate}: it should discard the packet sending
back a \texttt{SEGMENT\_CANCEL}.
\item The node is \emph{Free} and has free
links: it marks itself as \emph{Candidate} and forwards the \texttt{SEGMENT\_REQUEST}
to one of its free links, according to some internal ordering.
\item The node is \emph{CandidateStarting}: same as being \emph{Free},
since a segment request circulating in the network indicates that the
starting segment process has been completed.
\end{itemize}

@@

\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}}
When the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
the packet: the node set itself as \emph{Assigned} to the segment \emph{segID}. Further, it should forward this packet to the link where the
original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
can learn the id of the segment they belong to. Then, \emph{LED} should be
updated from \emph{tvisited} to \emph{visited}.

\subsection{Receiving a \texttt{SEGMENT\_CANCEL}}
When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that the research
for a segment along that path was unsuccessful. But if the
node still has some other free link to try, it should forward a
\texttt{SEGMENT\_REQUEST} to the those links. So a node forwards back
the \texttt{SEGMENT\_CANCEL} packet along the link that originated the
\texttt{SEGMENT\_REQUEST} packet \emph{only} when there are no more free
links to try. If this is the case, the node modifies its status from
\emph{Candidate} to \emph{Free} and forwards the
\texttt{SEGMENT\_CANCEL} packet to the link from which the request was
received. The process stops when the \texttt{SEGMENT\_CANCEL} packet
reach the starting node that originated the request.

### 2014-02-19 trunk/PAPER/simulation.tex
English fixes

% TODO: long paper
\subsection{Other Optimizations}
Some optimization parameters, which demonstrated to improve the \disr{}
results, have been fixed to some good values and are not subject to
further investigation in this paper; once again the focus here is not the
optimal setup of segments, but just demonstrating a working approach. 
These parameters are:
\begin{itemize}
\item \emph{cycle\_links}: max number of retries across the set of links of
each node. While searching for a free link due to an incoming \texttt{SEGMENT\_REQUEST},
the request itself is cancelled after a given number of tries. \hl{This
gives to the preceding node, that receives a \texttt{SEGMENT\_CANCEL}, the
chance to test a different path instead of waiting indefinitely.}
Default value is set to 1, i.e. each link is tried one time.
\item \emph{time to live (TTL)}: when a segment request is cancelled
along a certain path (using a \texttt{SEGMENT\_CANCEL}), a TTL field is
decreased in the request packet, so that requests that have been
denied too much times can desist, even if free links are
available. This is not only an optimization to shorten
requests' processes, but also solves some critical situations in which
request packets are blocked in routing loops in a particular path.
\item \emph{bootstrap\_timeout}: number of time units that a bootstrap node
should wait before assuming that a livelock in the starting segment
process has occurred. In the worst case, we can imagine that longest
path required is the one returning to the bootstrap node after having
traveled across all the links. So, although this is just an extreme
situation, a good upper limit can be safely be set to $N \times N$.
\item \emph{bootstrap\_immunity}: in order to avoid the failure of the whole \disr{}
setup process, a bootstrap node should not have defective links.
Enabling this optimization, a bootstrap node is immune to defects.
We may think about a pre-bootstrap phase that properly selects (from upper
layer via) a bootstrap node which is tested as properly connected. We
enabled this optimization, however empirical tests have shown us that only
simulations using bootstrap nodes placed on edges would be heavily
affected by similar issues since these nodes start with a lower number of links,
e.g. corner nodes could only have two connected direction, so even a \hl{single}
defective link could prevent a starting segment packet from coming back to the
bootstrap node to close the loop and create the \hl{first} segment.
\end{itemize}

>>>>

% TODO: long paper
\subsection{Other Optimizations}
Some optimization parameters, which demonstrated to improve the \disr{}
results, have been fixed to some good values and are not subject to
further investigation in this paper; once again the focus here is not the
optimal setup of segments, but just demonstrating a working approach. 
These parameters are:
\begin{itemize}
\item \emph{cycle\_links}: max number of retries across the set of links of
each node. While searching for a free link due to an incoming \texttt{SEGMENT\_REQUEST},
the request itself is cancelled after a given number of tries. This
gives to the preceding node on the path the
chance to test a different route instead of waiting indefinitely.
Default value is set to 1, i.e. each link is tried one time.
\item \emph{time to live (TTL)}: when a segment request is cancelled
along a certain path (using a \texttt{SEGMENT\_CANCEL}), a TTL field is
decreased in the request packet, so that requests that have been
denied too much times can desist, even if free links are
available. This is not only an optimization to shorten
requests' processes, but also solves some critical situations in which
request packets are blocked in routing loops in a particular path.
\item \emph{bootstrap\_timeout}: number of time units that a bootstrap node
should wait before assuming that a livelock in the starting segment
process has occurred. In the worst case, we can imagine that longest
path required is the one returning to the bootstrap node after having
traveled across all the links. So, although this is just an extreme
situation, a good upper limit can be safely be set to $N \times N$.
\item \emph{bootstrap\_immunity}: in order to avoid the failure of the whole \disr{}
setup process, a bootstrap node should not have defective links.
Enabling this optimization, a bootstrap node is immune to defects.
We may think about a pre-bootstrap phase that properly selects (from upper
layer via) a bootstrap node which is tested as properly connected. We
enabled this optimization, however empirical tests have shown us that only
simulations using bootstrap nodes placed on edges would be heavily
affected by similar issues since these nodes start with a lower number of links,
e.g. corner nodes could only have two connected direction, so even a single
defective link could prevent a starting segment packet from coming back to the
bootstrap node to close the loop and create the first segment.
\end{itemize}
